### 2023-08-14 chapters/main-contributions.tex
Update

\todo[options]{Update this paragraph according to the discussion of self-supervised learning for uncertainty estimation}
% \cite{nava_stateconsistency_2021, nava_uncertaintyaware_2021} Within robotics but not really related.

@@

An early version of this review paper \cite{borgholt_brief_2022} included a review of generative latent variable models for speech representation learning and a comparison between the two modelling paradigms. Due to the superior performance of self-supervised methods and a desire to focus on self-supervised methods, the paper in \cref{chp:paper-review} does not focus on generative latent variable models. The early version is included in \cref{app:paper-brief} for reference.

@@

Prior to this thesis, but relevant to mention in this section, we published work on question tracking for calls to emergency services using a multimodal approach that combines automatic transcripts with the raw audio \cite{havtorn_multiqt_2020}.

\contribitem{chp:paper-retrospective}

>>>>

\todo[inline]{Update this paragraph according to the discussion of self-supervised learning for uncertainty estimation}
% \cite{nava_stateconsistency_2021, nava_uncertaintyaware_2021} Within robotics but not really related.

@@

An early version of this review paper \cite{borgholt_brief_2022} included a review of generative latent variable models for speech representation learning and a comparison between the two modelling paradigms. Due to the superior performance of self-supervised methods and a desire to focus on self-supervised methods, the paper in \cref{chp:paper-review} does not focus on generative latent variable models. The early version is included in \cref{chp:appendix-paper-brief} for reference.

@@

Prior to this thesis, we published related work on question tracking for calls to emergency services using a multimodal approach that combines automatic transcripts with the raw audio \cite{havtorn_multiqt_2020}.

\contribitem{chp:paper-retrospective}
Effective stroke treatment depends on recognition by call-takers at prehospital telehealth services. This paper aimed to develop and assess the potential of machine learning in improving prehospital stroke recognition during medical helpline calls. 
We used calls from Copenhagen during 2015 to 2020, to develop a machine learning-based classification pipeline. First, calls are transcribed by a speech recognition model and then categorised as stroke or non-stroke using a text classification model.
On test data from 2021, call-takers achieved an overall sensitivity of 52.7\% (95\% confidence interval 49.2-56.4\%) with a positive predictive value (PPV) of 17.1\% (15.5-18.6\%) while the machine learning framework performed significantly better (p < 0.0001) with a sensitivity of 63.0\% (62.0-64.1\%) and a PPV of 24.9\% (24.3-25.5\%).
This study provides preliminary evidence that a machine learning framework for recognizing stroke in prehospital medical helpline calls could become a supportive tool for call-takers, aiding in early and accurate stroke recognition.
